Load packages
```{r results = "hide" }
# Clear workspace
rm(list=ls())
#load general libraries
library(tidyverse)
```



```{r}
getwd()
# List all the .csv files in the directory
csv_files <- list.files(path = "../input", pattern = "\\.csv$")
file <- character()

# Loop through the list of .csv files and read them into variables
for (file in csv_files) {
  # Remove the file extension to use as the variable name
  var_name <- sub("\\.csv", "", file)
  # Read the .csv file into a variable with the same name
  assign(var_name, read.csv(paste0("../input/",file)))
}

#Making the leftmost column rownames
rownames(Articles)<-Articles$Document 
Articles <-select(Articles, -Document)

Articles<-Articles %>% mutate(keywords=paste(Discipline,Substance,Model.Study,Endpoint,Tool, ImAnalysis,sep=", "))


```

Preprocessing control to make sure there are no blank spaces at the start or end of each char string
```{r}
trim_spaces <- function(input) {
  if (is.data.frame(input)) {
    # Initialize DataFrame with the same number of rows
    trimmed_df <- data.frame(matrix(ncol = ncol(input), nrow = nrow(input)))
    colnames(trimmed_df) <- colnames(input)

    # Apply trimming to each column of the DataFrame
    for (col in names(input)) {
      trimmed_df[[col]] <- if (is.character(input[[col]])) trimws(input[[col]]) else input[[col]]
    }
    
    return(trimmed_df)
  }else {
    stop("Input must be a dataframe")
  }
}

Classfull<-trim_spaces(Classfull)
```



Another form of object - list:
```{r}
Articlist <- Articles 
# Split and convert to a list within the dataframe
Articlist$keywords <- lapply(Articlist$keywords, function(x) strsplit(x, ",\\s*")[[1]])
Articlist<-Articlist$keywords
names(Articlist)<-rownames(Articles)
```


#Add all data from WoS
```{r}
#Import 
tox <- readRDS(paste0("../input/","tox.RDS"))

#try ma5ching
all(rownames(Articles) %in% rownames(tox))
#combine
Artful <- merge(Articles,tox[rownames(Articles),], by = "row.names")

```

Remove unnecessary variables, except those we will use

```{r}
rm(list=setdiff(ls(), c("Classfull", "Artful", "Articlist")))
```

Preprocessing for analysis

```{r}
#If I want to add a second series of lists. 
#Art2<-Articlist
#Art2[["ClassInd"]] <- Articlist

# Instead, I want to create two more twin char lists with terms
Art3 <- mapply(function(char_vec, related_data) list(char_vec, related_data, related_data),
                        Articlist, Articlist, SIMPLIFY = FALSE)

rm(Articlist)

```

Open one by one keyterms and scan through the hierarchy to identify the class of the term and it's ID (row number in hierarchical classification table)
```{r}
#Load a thesaurus list of synonyms
#thesaurus<-read.csv("../input/thesaurus.csv")
#Create a function 
scanli<- function (scannedimp,refclass){
  scanned<-scannedimp
  #Loop through every group of three related sublists
  for (i in 1:length(scanned)){
    #Loop through every string element of the char vector
    for (j in 1:length(scanned[[i]][[1]])){
      #first check if term is in thesaurus
     if (any(which(thesaurus == scanned[[i]][[1]][[j]], arr.ind = TRUE))){}
      #Serach through the reference hierarchical table and fill in first the class [[2]] and then index [[3]]
      scanned[[i]][[2]][[j]]<-paste0("Class",which(refclass == scanned[[i]][[1]][[j]], arr.ind = TRUE)[2]) #the last index is for the columns - class
      
      scanned[[i]][[3]][[j]]<-which(refclass == scanned[[i]][[1]][[j]], arr.ind = TRUE)[1] #the last index is for the rows - id
    }
  }
  return(scanned)
}

scannedimp<-Art3
refclass<-Classfull

length(Art3)
Art3<-scanli(Art3,Classfull)
```
NB! Optional step: remove articles with "NO IMAGE ANALYSIS" (ID=144 in Classfull)
```{r results = "hide" }
#Anyway, ccheck ID
which(Classfull == "no image analysis", arr.ind = TRUE)[,1]
#OK, go on
Art3_iman<-Art3
Art3_garb <- list()
report_noim<-data.frame()

  for(i in 1:length(Art3)){
    if(any(grepl(144,Art3[[i]][[3]]))){
      
      r<-nrow(report_noim)
        Art3_iman<-Art3_iman[setdiff(names(Art3_iman), names(Art3)[i])]
        report_noim[r+1,1]<-names(Art3)[i]
      print(i)
      
      Art3_garb<-append(Art3[i],Art3_garb)
    }
    print(paste0("a",i))
    }
#Continue with only a List of Articles WITH Image Analysis
Art3<-Art3_iman
```


Map the articles to IDs in classification now

```{r}
# Create a data.frame from the list of lists with named columns, excluding NA values
Art4 <- do.call(rbind.data.frame, Art3)
colnames(Art4)<-c("Term","Class","IDs") 
Art4<-Art4[!is.na(Art4$IDs),]
#check for empty spaces
which(Art4$Term=="")
which(Art4$Class=="")
which(Art4$IDs=="")
#Remove empty spaces, which I saw are only in the Terms column
Art4<-Art4[-which(Art4$Term==""),]
```

Prepare the selection of columns for the articles table
```{r}
rownames(Artful)<-Artful$Row.names
Artful<- Artful %>% mutate(keyIDs=keywords, keyClass=keywords) %>% select(TI, Year, Local.Citations, Normalized.Local.Citations, keywords, keyIDs, keyClass)
```

Explore classes - Explore First Class First
```{r}
# Creating a grouped summary table
summary_table <- Classfull %>%
  group_by(Class1) %>%
  summarize(Count = n())

# Print the summary table
print(summary_table)
```
Explore classes - Explore Second Class 
```{r}
# Creating a grouped summary table
summary_table2 <- Classfull[which(Classfull$Class1=="tool"),] %>%
  group_by(Class2) %>%
  summarize(Count = n())

# Print the summary table
print(summary_table2)
```

Explore classes - Explore Third Class 
```{r}
# Creating a grouped summary table
summary_table3 <- Classfull[which(Classfull$Class2=="increased dimensionality imaging"),] %>%
  group_by(Class3) %>%
  summarize(Count = n())

# Print the summary table
print(summary_table3)
```

Explore classes - Explore 4th Class 
```{r}
# Creating a grouped summary table
summary_table4 <- Classfull[which(Classfull$Class3=="open source"),] %>%
  group_by(Class4) %>%
  summarize(Count = n())

# Print the summary table
print(summary_table4)
```

Clear unnecessary data
```{r}
rm(list=setdiff(ls(), c("Classfull", "Artful", "Art3", "Art4")))
```

#Create final reports
```{r}
#Prepare article reference list
Art5<-Art4 %>% mutate(Row.Names=gsub("\\..*","",rownames(.))) 
Artful<- Artful %>% mutate(Row.Names=rownames(.))
Art5<-merge(Art5, Artful, by = "Row.Names", all.x = TRUE) %>% select(Row.Names,IDs,Class,Term,Year,Normalized.Local.Citations,TI)
#prepare major list to combine all data
MajorClass<-"increased dimensionality imaging" #which column does it belong in the original hierarchical table
MajorClassRank<-2
cmd<-paste0("Subclasses<-unique(Classfull$Class",MajorClassRank+1,"[which(Classfull$Class",MajorClassRank,"==MajorClass)])")
Subclasses<-eval(parse(text = cmd))

ClassChoice<-list(Class1=MajorClass,Class2=Subclasses)
#Add Sublists for IDs and Etc to ClassChoice Categories
ClassChoice$Class2<-list(Term=ClassChoice$Class2, IDrange=as.list(ClassChoice$Class2),Title=as.list(ClassChoice$Class2),
                         Citat.Norm=as.list(ClassChoice$Class2), Year=as.list(ClassChoice$Class2))

#Make deeper hyerarchical level sublists in the format list
for(z in 1:length(ClassChoice[["Class2"]])){
      for(t in 1:length(ClassChoice[["Class2"]][[z]])){ 
        ClassChoice[["Class2"]][[z]][[t]]<-list(ClassChoice[["Class2"]][[z]][[t]])
        }}
#Function to loop through and fill in the data
idclass<-function(ClassChoice,Classfull,Art5){
  
     for (i in 1:length(ClassChoice[[2]][[1]])){
       
    cmd2<-paste0("ClassChoice[['Class2']][['IDrange']][[i]]<-which(Classfull$Class",MajorClassRank+1,"==ClassChoice[['Class2']][['Term']][[i]])")
eval(parse(text = cmd2))  

     }
   for (i in 1:length(ClassChoice[[2]][[1]])){
    for (j in 1:length(ClassChoice[["Class2"]][["IDrange"]][[i]])){
     # ClassChoice[["Class2"]][[i]][[j]][[1]]<-as.list(ClassChoice[["Class2"]][[i]][[j]][[1]])
    ClassChoice[["Class2"]][["Title"]][[i]][[j]]<-Art5$TI[which(Art5$IDs==ClassChoice[["Class2"]][["IDrange"]][[i]][[j]])]
    print(paste0(i,":class ",j,":sub"))
    
    ClassChoice[["Class2"]][["Citat.Norm"]][[i]][[j]]<-Art5$Normalized.Local.Citations[which(Art5$IDs==ClassChoice[["Class2"]][["IDrange"]][[i]][[j]])]
    
    ClassChoice[["Class2"]][["Year"]][[i]][[j]]<-Art5$Year[which(Art5$IDs==ClassChoice[["Class2"]][["IDrange"]][[i]][[j]])]
      }}
  return(ClassChoice)
}
#Execute the function
ClassChoice <- idclass(ClassChoice,Classfull,Art5)
#Save data structure
rio::export(ClassChoice,paste0("../input/","ClassChoice[[1]],".RDS"))

```


#Create stat summary:
```{r}
#Flatten:
flat.extr<-function(ClassChoice){
#Create a Empty DataFrame with 0 rows and n columns
columns <- c("Term","Title","Year","Citat.Norm")
flatdf <- data.frame(matrix(nrow = 0, ncol = length(columns))) 
colnames(flatdf) <- columns
#Now write the loop to extract info from the list and organize it in the flat df
  for(i in 1:length(ClassChoice[[2]][[2]])){
    
    for(j in 1:length(ClassChoice[[2]][[3]][[i]])){
      
       for(t in 1:length(ClassChoice[[2]][[3]][[i]][[j]])){
         
         if(length(ClassChoice[[2]][[3]][[i]][[j]])!=0){
         
    temp<-nrow(flatdf)+1
      flatdf[temp,"Term"] <- ClassChoice[[2]][[1]][[i]]
      flatdf[temp,"Title"] <- ClassChoice[[2]][[3]][[i]][[j]][[t]]
      flatdf[temp,"Year"] <- ClassChoice[[2]][[5]][[i]][[j]][[t]]
      flatdf[temp,"Citat.Norm"] <- ClassChoice[[2]][[4]][[i]][[j]][[t]]
      print(paste0(i,",",j,",",t,",",nrow(flatdf)))
      }else{
        flatdf[temp,"Title"] <- NA
      flatdf[temp,"Year"] <- NA
      flatdf[temp,"Citat.Norm"] <- NA
      print(paste0("Zero Error:",i,",",j,",",t,",",nrow(flatdf)))       
      }
    }}}
return(na.omit(flatdf))
}
#Now apply the function
flatdf<-flat.extr(ClassChoice)
```

Preprocessing and saving the flat df table
```{r}
# Identifying duplicate rows (considering all columns)   
remove_duplicate_rows <- function(dataframe){
  #Keeping the first occurrence and removing the rest
  dataframe[!duplicated(dataframe), ]
  }  
#Use the function to remove duplicate rows  
flatdf <- remove_duplicate_rows(flatdf)
flatdf<-flatdf %>% mutate(across(everything(), ~na_if(., "NA"))) %>% #make sure NAs aren't just strings
  na.omit() %>% mutate(across(c("Year", "Citat.Norm"), as.numeric))

#Save as RDS object
rio::export(flatdf,paste0("../input/","ClassChoice[[1]],"_Flat.RDS"))
```

Transform and analyze
```{r}
length(unique(flatdf$Title))
#Calculate the percent of duplicated overlapping categories:
perc.dupl<-(sum(duplicated(flatdf$Title))/length(flatdf$Title))*100

#Make article titles unique
flat_wide<- flatdf %>% pivot_wider(names_from = "Term", 
              names_prefix = "Split:",
              values_from = "Term")

#Make an analysis, highlighting single discipline vs multidisciplinary research
#Split table:
flat_single <- flatdf %>%
  group_by(Title) %>%
  filter(n() == 1) %>%
  ungroup()
#Test
sum(duplicated(flat_single$Title))

flat_multi <- flatdf %>%
  group_by(Title) %>%
  filter(n() > 1) %>%
  distinct(Title, .keep_all = TRUE) %>%
  ungroup()
#Test
sum(duplicated(flat_single$Title))
intersect(flat_multi$Title, flat_single$Title)

#Compare multidisciplinary and single discipline research
t.test(flat_multi$Citat.Norm,flat_single$Citat.Norm)


```
Graphical exploration, created with esquisse - For the "Discipline term":

```{r}

library(ggplot2)

ggplot(flatdf) +
 aes(x = Term) +
 geom_bar(fill = "#112446") +
 theme_minimal()

ggplot(flatdf) +
 aes(x = Year, fill = Term) +
 geom_histogram(bins = 30L) +
 scale_fill_hue(direction = 1) +
 theme_minimal()

ggplot(flatdf) +
 aes(x = Year, fill = Term) +
 geom_histogram(bins = 30L) +
 scale_fill_hue(direction = 1) +
 theme_minimal()

ggplot(flatdf) +
 aes(x = Citat.Norm, fill = Term) +
 geom_histogram(bins = 30L) +
 scale_fill_hue(direction = 1) +
 theme_minimal()

ggplot(flatdf) +
 aes(x = Year, y = Citat.Norm, colour = Term) +
 geom_point(shape = "circle", size = 4L) +
 scale_color_hue(direction = 1) +
 theme_minimal()


```
